### 2017-10-10 manuscript.rmd
minor tweeks

	# Graphics
	library( cowplot )
	library( ggtree )
	library( GGally )
	library( fields ) # tim.colors
	library( seriation )
	library( gridExtra )
	library( RGraphics )
  library( factoextra )
  library( FactoMineR )

	# Biological
	library( edgeR )
	library( treeio )
	library( hutan )	# https://github.com/caseywdunn/hutan
	library( ape )
	library( agalmar )	# https://github.com/caseywdunn/agalmar
	library( picante )  # cor.table
	library( phytools ) # phylosig
  library( vegan )
  library( ggtree )
  library( phangorn )
  library( geiger )
  library( phylobase )
  library( adephylo )
  library( geomorph ) #physig
  library( phylolm )

@@

```{r char_evo_setup, include=F, echo=F}
#Working directory
setwd("~/Dropbox/siphonophore_phylogeny_2017/character_coding")

#Load data
read.csv('main_characters.csv', header = T, sep = ',') -> cdata
rownames(cdata) = cdata$Species

#Load tree
tree = species_ultrametric
tree$tip.label = str_replace_all(tree$tip.label,'_',' ')
tree <- drop.tip(tree, which(!(tree$tip.label %in% rownames(cdata))))
ultratree <- chronos(tree)

>>>>

	# Graphics
	library( cowplot )
	library( ggtree )
#	library( GGally )
	library( fields ) # tim.colors
	library( seriation )
	library( gridExtra )
#	library( RGraphics )
  library( factoextra )
  library( FactoMineR )

	# Biological
#	library( edgeR )
	library( treeio )
	library( hutan )	# https://github.com/caseywdunn/hutan
	library( ape )
#	library( agalmar )	# https://github.com/caseywdunn/agalmar
	library( picante )  # cor.table
	library( phytools ) # phylosig
  library( vegan )
  library( ggtree )
  library( phangorn )
  library( geiger )
  library( phylobase )
  library( fields )
  library( adephylo )
  library( geomorph ) #physig
  library( phylolm )

@@

```{r char_evo_setup, include=F, echo=F}

#Load data
read.csv('character_coding/main_characters.csv', header = T, sep = ',') -> cdata
rownames(cdata) = cdata$Species

#Load tree
tree = species_ultrametric
tree$tip.label = str_replace_all(tree$tip.label,'_',' ')
tree <- drop.tip(tree, which(!(tree$tip.label %in% rownames(cdata))))
ultratree <- chronos(tree)
class( ultratree ) = "phylo"
